\forestclaw: Hybrid forest-of-octrees AMR for hyperbolic conservation laws

### 2013-10-31 docs/parco13/paper.tex
Use latest sphere strong scaling results
Two tweaks

\begin{table}
  \begin{center}
   \begin{tabular}{l|rrrrrr}
      $P$ (\# total MPI ranks) & 16 & 64 & 256 & 1,024 & 4,096 & 16,384 \\
      \hline
      par.\ efficiency (\%) & 100 & 96 & 96 & 103 & 103 & 82 \\
    \end{tabular}
  \end{center}
  \caption{Weak scalability on a uniform mesh from level 6 at 64 cores to level
    11 at 16,384
    % using
    (16 MPI ranks/node).}%
  \label{tab:weakscale}
\end{table}%
%
We have examined weak scalability as well by using four times as many MPI
processes for each level increase.
% , from level 6 at 64 cores to level 11 at 16,384.
Up to 4,096 cores, the exchange times stay consistently below 16\% of the time
integration,
% and the time in seconds per time integration step varies between
% .0578 and .0602,
and we obtain optimal parallel efficiency.  For
% the data point at
16,384 cores, the efficiency reduces to 82\%
with the current code (see \Tab{weakscale}).

@@

\begin{figure}
  \begin{center}
    \hspace{.1\columnwidth}
    \begin{minipage}[c]{.30\columnwidth}
      \includegraphics[width=\columnwidth]{../figs_misc/sphere_partition5}
    \end{minipage}
    \hspace{.05\columnwidth}
    \begin{minipage}[c]{.4\columnwidth}
    \begin{tabular}{r|r}
       $P$ & time int./step \\
      \hline
       16 & 1.115 \\
       32 & 0.557 \\
       64 & 0.297 \\
      256 & 0.092 \\
    \end{tabular}
  \end{minipage}
\end{center}
\caption{Left: Partition of the spherical Example 2 between five
  MPI processes, indicated by the color scale, at simulated time $T = 1$.
  % The  partition shows the mesh equator,
  The refinement is invariant under the parallel partition
  and follows the front, which is not aligned with the equator.  Right: Strong scaling
  for a uniform run at level 8.}
\label{fig:spherical}
\end{figure}
To showcase a multiblock connectivity, we include results for the spherical Example 2 in
\Fig{spherical}, together with a strong scaling table from 16 to 256 MPI ranks.

>>>>

\begin{table}
  \begin{center}
   \begin{tabular}{l|rrrrrr}
      $P$ (\# total MPI ranks) & 16 & 64 & 256 & 1,024 & 4,096 & 16,384 \\
      \hline
      par.\ efficiency (\%) & 100 & 96 & 96 & 103 & 103 & 82 \\
    \end{tabular}
  \end{center}
  \caption{Weak scalability on a uniform mesh from level 6 at 64 cores to level
    11 at 16,384
    % using
    (16 MPI ranks/node).}%
  \label{tab:weakscale}
\end{table}%
%
We examine weak scalability as well by using four times as many MPI
processes for each level increase.
% , from level 6 at 64 cores to level 11 at 16,384.
Up to 4,096 cores, the exchange times stay consistently below 16\% of the time
integration,
% and the time in seconds per time integration step varies between
% .0578 and .0602,
and we obtain optimal parallel efficiency.  For
% the data point at
16,384 cores, the efficiency reduces to 82\%
with the current code (see \Tab{weakscale}).

@@

\begin{figure}
  \begin{center}
    %\hspace{.1\columnwidth}
    \begin{minipage}[c]{.3\columnwidth}
      \includegraphics[width=\columnwidth]{../figs_misc/sphere_partition5}
    \end{minipage}
    \hspace{3ex}
    \begin{minipage}[c]{.44\columnwidth}
    \begin{tabular}{rcr}
      \multicolumn{1}{c}{$P$}
      & time int./step (s) & eff.\ (\%) \\
      \hline
         16 & 3.539  & 100.0 \\
       % 32 & 1.763  &  99.6 \\
         64 & 0.889  & 100.5 \\
      % 128 & 0.445  & 100.6 \\
        256 & 0.223  & 100.7 \\
      1,024 & 0.055 & 100.2 \\
      4,096 & 0.014 &  99.4 \\
% old results
%        16 & 1.115 \\
%        32 & 0.557 \\
%        64 & 0.297 \\
%       256 & 0.092 \\
    \end{tabular}
  \end{minipage}
\end{center}
\caption{Left: Partition of the spherical Example 2 between five
  MPI processes, indicated by the color scale, at simulated time $T = 1$.
  % The  partition shows the mesh equator,
  The refinement is invariant under the parallel partition
  and follows the front, which is not aligned with the equator.  Right: Strong scaling
  for a uniform run at level 8.}
\label{fig:spherical}
\end{figure}
To showcase a multiblock connectivity, we include results for the spherical Example 2 in
\Fig{spherical}, together with a strong scaling table from 16 to 4,096 MPI ranks.
